Modern Graph Generators: A Survey

### 2018-11-25 generators_SocialNetworks.tex
Sherif Changes

Another important aspect
of social networks is the community effect. A detailed study of structure of
communities in 70 real-world networks is provided, e.g., in
~\cite{Leskovec:2008:SPC:1367497.1367591}.
~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyzed the structure of
communities (clustering coefficient, triangle participation ratio, bridges,
diameter, conductance and size) in both real-world graphs and outputs of existing graph
generators LFR~\cite{PhysRevE.78.046110} and the
LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. They discover that communities found in different graphs follow quite similar distributions and that communities in a single graph have diverse nature and are difficult to fit with a single model.

@@

\paragraph{Cloning of Social Networks} Paper~\cite{Sukthankar-SocialInfo2014}
introduces a synthetic network generator designed for cloning social network
statistics of an existing dataset. The network starts with a small number of
nodes, and new nodes are added until the network reaches the required number. It
has two basic parameters: homophily and link density. A high \emph{homophily}
value indicates that links are more likely to be formed between nodes with the
same label; these labels can be viewed as being equivalent to community
membership.

>>>>

Another important aspect
of social networks is the community effect. A detailed study of structure of
communities in 70 real-world networks is provided, e.g., in
~\cite{Leskovec:2008:SPC:1367497.1367591}.
~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyzed the structure of
communities (clustering coefficient, triangle participation ratio, bridges,
diameter, conductance and size) in both real-world graphs and outputs of existing graph
generators LFR~\cite{PhysRevE.78.046110} and the
LDBC-SNB~\cite{Erling:2015:LSN:2723372.2742786}. They found out that discovered communities  in different graphs have common distributions and that communities in a single graph have diverse nature and are difficult to fit with a single model.

@@

\paragraph{Cloning of Social Networks} ~\cite{Sukthankar-SocialInfo2014}
introduced a synthetic network generator designed for cloning social network
statistics of an existing dataset. The network starts with a small number of
nodes, and new nodes are added until the network reaches the required number. It
has two basic parameters: homophily and link density. A high \emph{homophily}
value indicates that links are more likely to be formed between nodes with the
same label; these labels can be viewed as being equivalent to community
membership.
